Accounting for uncertainty in simulating greenhouse gas emissions from dairy cattle in Kenya

### 2022-06-22 Manuscript_figures.Rmd
mainly emissions intensity -> emission intensity

```{r, warning=FALSE, message=FALSE,fig.dim = c(8, 4), fig.cap = "***Figure 1.*** *Estimated total emissions from livestock (a) and emissions intensity of milk production (b) for a smallholder dairy farm in Kenya. Plausible estimates of both metrics are generated through Monte Carlo simulation, based on 1000 runs of a greenhouse gas emissions model, with uncertainty introduced by specifying inputs as probability distributions. The blue line indicates a precise estimate based on precise results from a farm survey and default parameters recommended by various guidance documents.*"}

@@

farm5b<-ggplot(data=farm5_emissions$y, aes(CO2eq_per_milk)) +
geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") +
  ylab("Relative probability") +
    xlab(expression(Emissions~intensity~(kg~CO[2]*'-eq'~kg^-1))) + ggtitle("b) Emissions intensity")

@@

```{r, warning=FALSE, message=FALSE, fig.dim = c(8, 4), fig.cap = "***Figure 2.*** *Total greenhouse gas emissions from livestock (a) and emissions intensity of milk production (b) across 4140 simulated livestock-keeping households in Kenya (informed by data collected on 414 farms). Plausible estimates of both metrics are generated through Monte Carlo simulation, based on 1000 runs of a greenhouse gas emissions model, with uncertainty introduced by specifying inputs as probability distributions.*"}

@@

all_farms_intensity<-ggplot(data=GHG_simulation_scenarios$y, aes(CO2eq_per_milk)) +
geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") +
  ylab("Relative probability") + theme_bw() +
    xlab(expression(Emissions~intensity~(kg~CO[2]*'-eq'~kg^-1))) + ggtitle("b) Emissions intensity")

@@

We can now look at summary statistics of total and per head emissions from cattle across livestock-keeping smallholder farms in Kenya. To exclude farms that do not appear to be specializing in livestock, some of which feature extremely high (up to infinity in cases where no milk is produced) emissions intensity, we also look at summary statistics across only the farms with per head milk yields of >500 kg of milk.

@@

emissions_summary<-rbind(data.frame("Emissions per farm"=round(quantile(GHG_simulation_scenarios$y$on_farm,
                                                                  c(0,0.05,0.5,0.95,1))/1000,1),
                                    "Emissions per head"=round(quantile(GHG_simulation_scenarios$y$pc_on_farm,
                                                                    c(0,0.05,0.5,0.95,1))/1000,1),
                                    "Emissions intensity"=round(quantile(GHG_simulation_scenarios$y$CO2eq_per_milk,
                                                                   c(0,0.05,0.5,0.95,1)),1)),
                         data.frame("Emissions per farm"=round(quantile(dairy_households$y$on_farm,
                                                                  c(0,0.05,0.5,0.95,1))/1000,1),
                                    "Emissions per head"=round(quantile(dairy_households$y$pc_on_farm,
                                                                    c(0,0.05,0.5,0.95,1))/1000,1),
                                    "Emissions intensity"=round(quantile(dairy_households$y$CO2eq_per_milk,
                                                                   c(0,0.05,0.5,0.95,1)),1)))
emissions_summary$Quantile<-c("Minimum","5% quantile", "Median", "95% quantile", "Maximum",
                              "Minimum","5% quantile", "Median", "95% quantile", "Maximum")
rownames(emissions_summary)<-NULL

kable(emissions_summary[,c(4,1,2,3)], booktabs = TRUE,
      col.names = c("Distribution attribute",
                    paste0("CO","$_2$","-eq farm","$^{-1}$"),
                    paste0("CO","$_2$","-eq head","$^{-1}$"),
                    paste0("CO","$_2$","-eq kg","$^{-1}$")),
      caption = "<p style='color:black'><i><b>Table S3.</b> Summary statistics of simulated greenhouse gas emissions from cattle across a population of cattle-keeping smallholder farms in Kenya</i></p>") %>% pack_rows(
  index = c("Emissions per farm" = 5, "Emissions per dairy-focused farm" = 5), background="lightgray") %>%
column_spec(2:4, width = "5cm") %>% row_spec(0, align = "c") %>% 
  add_header_above(c(" " = 1, "Emissions per farm" = 1, "Emissions per head" = 1, "Emissions intensity" = 1))

@@

We're interested in the suitability of total per head milk production per year as an indicator of the greenhouse gas emissions intensity of milk production.

@@

```{r, warning=FALSE, message=FALSE, fig.dim = c(8, 6), fig.cap="***Figure 3.***  *Relationship between milk yield per head (x-axis) and emissions intensity of milk production for livestock-keeping smallholder households in Kenya, expressed as a population-level scatter plot (a) and an interpolated probability density surface (b). The vertical lines in (b) illustrate slices through the density surface at productivity levels of 2000 (red) and 3000 (blue) kg milk head^-1^ year^-1^ (the corresponding distributions are shown in Fig. 4b).*"}

plot1 <- ggplot(dairy_households$y, aes(x = pc_milk_yield, y = CO2eq_per_milk)) + 
  geom_point(shape = 20, color = "blue", size = 2) + 
  stat_smooth(method = "loess", fullrange = TRUE) +
  geom_density_2d() +
  geom_rug(color="lightskyblue3") + 
  labs(y=expression(Emissions~intensity~of~milk~production~(kg~CO[2]*'-eq'~kg^{-1})),
       x=expression(Milk~yield~per~head~(kg~head^{-1}~year^{-1})))+
  theme_bw() +
  theme(legend.position = c(0.15, 0.9))

@@

densi<-ggplot(dairy_households$y, aes(x = pc_milk_yield, y = CO2eq_per_milk)) +
  stat_density_2d(
    geom = "raster",
    aes(fill = after_stat(density)),
    contour = FALSE
    ) +
  scale_fill_viridis_c() + 
  labs(y=expression(Emissions~intensity~of~milk~production~(kg~CO[2]*'-eq'~kg^{-1})),
       x=expression(Milk~yield~per~head~(kg~head^{-1}~year^{-1})),
       fill="Probability \ndensity") +
  theme_bw() + geom_vline(xintercept=c(2000,3000),color=c("#F8766D","#00BFC4"),alpha=.5, lwd=2)

@@

ggsave("figures/Fig_3_scatter_and_surface_per_head_milk_emissions_intensity.png",width=10,height=6)

@@

According to these distributions, the emissions intensity at a particular per head milk yield can be described by a slice through the probability surface.

```{r varkernelslicerange, message=FALSE, warning=FALSE, fig.dim = c(12, 4), fig.cap="***Figure 4.*** *Greenhouse gas emissions intensity of milk production at specific levels of per-head milk production among livestock-keeping smallholder farms in Kenya. Distributions are shown for (a) a production level of 2000 kg milk head^-1^ year^-1^, including a histogram of the random samples the distribution is based on, and (b) production levels of 2000 and 3000 kg milk head^-1^ year^-1^.*"}
slice_2000<-uncertainty::varslice_resample(in_var = dairy_households$y$pc_milk_yield,
                                 out_var = dairy_households$y$CO2eq_per_milk, 
                                 expectedin_var=2000,
                           n = 1000,
                           n_samples = 1000,
                           out_var_sampling = 1000)
slice_3000<-uncertainty::varslice_resample(in_var = dairy_households$y$pc_milk_yield,
                                 out_var = dairy_households$y$CO2eq_per_milk, 
                                 expectedin_var=3000,
                           n = 1000,
                           n_samples = 1000,
                           out_var_sampling = 1000)

one_slice<-ggplot(data=data.frame(CO2eq_per_milk=slice_2000$resampled), aes(CO2eq_per_milk)) +
geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") +
  ylab("Relative probability") +
    xlab(expression(Emissions~intensity~at~2000~kg~milk~per~head~(kg~CO[2]*'-eq'~kg^-1))) + theme_bw() + ggtitle("a) Slice through the emissions intensity distribution")

@@

two_slices<-ggplot(data=slices, aes(Values, fill=Level)) +
 geom_density(alpha=.2) +
  ylab("Relative probability") +
    xlab(expression(Emissions~intensity~at~specific~milk~yield~per~head~(kg~CO[2]*'-eq'~kg^-1))) + labs(fill='Productivity level') + theme_bw() + ggtitle("b) Two slices at different productivity levels")

@@

```{r, fig.dim = c(8, 4), fig.cap="***Figure 5.*** *Probability of a particular farm B featuring lower emissions intensity of milk production than another farm A, based on observed per-head milk production levels. Estimates are derived from pairwise comparisons of slices through a population-wide generalization surface of the relationship between per-head milk production and emissions intensity. This generalization was generated through Monte Carlo simulation, based on scenarios representing observed production settings on 414 livestock-keeping smallholder farms in Kenya.*"}

@@

ggplot(data = decreased_emissions_probability, aes(Base_yield, new_yield)) + geom_contour_filled(aes(z =
                                                      probability)) +
  ggtitle("Probability of lower emissions intensity on farm B") + 
  labs(y=expression(Milk~yield~of~farm~B~(kg~head^{-1}~year^{-1})),
       x=expression(Milk~yield~of~farm~A~(kg~head^{-1}~year^{-1})),
       fill="Probability of \nlower emissions \nintensity on farm B") +
  stat_contour(aes(z = probability),breaks = c(0.9),col="black") + 
  theme_bw() +
  scale_x_continuous(limits=c(min(decreased_emissions_probability$Base_yield),NA),expand = c(0, 0)) +
  scale_y_continuous(limits=c(min(decreased_emissions_probability$new_yield),NA),expand = c(0, 0))

ggsave("figures/Fig_5_probability_of_lower_emissions_intensity.png", width=7,height=5)

@@

```{r, warning=FALSE, fig.dim = c(8, 4), fig.cap="***Figure S2.*** *Probability of a particular farm B featuring lower emissions intensity of milk production than another farm A, based on observed per-head milk production levels (see caption to Fig. 5 for more details). The red line indicates a confidence threshold that is based on the 95% confidence interval of the LOESS regression line shown in Fig. 3a. Using this threshold for predicting changes in emissions intensity based on milk yield data would likely lead to a lot of inaccurate classifications.*"}

ggplot(data = decreased_emissions_probability, aes(Base_yield, new_yield)) + geom_contour_filled(aes(z =
                                                      probability)) +
  ggtitle("Probability of lower emissions intensity on farm B") + 
  labs(y=expression(Milk~yield~of~farm~B~(kg~head^{-1}~year^{-1})),
       x=expression(Milk~yield~of~farm~A~(kg~head^{-1}~year^{-1})),
       fill="Probability of \nlower emissions \nintensity on farm B") +
  stat_contour(aes(z = probability),breaks = c(0.9),col="black") + 
  geom_smooth(data=prediction_data, aes(x=x,y=min_more_milk_loess),col="red")  +  geom_abline(slope=1,intercept=0,linetype = "dashed")  +
  theme_bw() +
  scale_x_continuous(limits=c(min(decreased_emissions_probability$Base_yield),NA),expand = c(0, 0)) +
  scale_y_continuous(limits=c(min(decreased_emissions_probability$new_yield),NA),expand = c(0, 0))

ggsave("figures/Fig_S2_probability_of_lower_emissions_intensity.png", width=7,height=5)

@@

```{r, fig.dim = c(8, 8), fig.cap="***Figure S4.*** *Intervention impact on per head milk production and greenhouse gas emissions intensity.*"}

@@

interventions[,"milk_change"]<-interventions$pc_milk_yield-interventions$pc_milk_baseline
interventions[,"emissions_intensity_change"]<-interventions$CO2eq_per_milk-interventions$CO2_intensity_baseline
interventions[,"milk_change_relative"]<-(interventions$pc_milk_yield-interventions$pc_milk_baseline)/interventions$pc_milk_baseline*100
interventions[,"emissions_intensity_change_relative"]<-
  (interventions$CO2eq_per_milk-interventions$CO2_intensity_baseline)/interventions$CO2_intensity_baseline*100

@@

intervention_change <- merge(data.frame(aggregate(interventions_normal_milk$emissions_intensity_change,
                                                  by = list(interventions_normal_milk$intervention),
                                                  FUN = mean)),
                             data.frame(aggregate(interventions_normal_milk$milk_change,
                                                  by = list(interventions_normal_milk$intervention),
                                                  FUN = mean)),
                             by = "Group.1")
colnames(intervention_change) <-
  c("intervention", "emissions_intensity_change", "milk_change")

@@

interventions_scatter<-ggplot(data=interventions_normal_milk,
                        aes(x=milk_change,y=emissions_intensity_change)) +
  geom_point(aes(color=intervention),size=0.9) +
  theme_bw() +
  ggtitle("Intervention impact on milk yield and emissions") + 
  labs(y=expression(Change~'in'~emissions~intensity~(kg~CO[2]*'-eq'~kg^-1)),
       x="Change in per head milk yield (kg)",
       color="Intervention") +
  scale_color_manual(values= c("breed" = intervention_colors[1],
                              "nobull" = intervention_colors[2],
                              "lessReplace" = intervention_colors[3],
                              "Calliandra" = intervention_colors[4],
                              "balance" = intervention_colors[6]),
                    labels = c("Breed change", "No bulls", "Fewer males", "Calliandra feed", "Balanced diet")) +
  facet_wrap(~factor(intervention,
                     levels=c("breed","nobull","lessReplace","Calliandra","balance"),
                     labels=c("Breed change", "Retire unproductive bulls", "Fewer replacement males", "Calliandra feed", "Balanced diet"))  ) +
  theme(legend.position = "none")

@@

```{r, fig.dim = c(8, 8), fig.cap="***Figure 6.*** *Intervention impacts on relative per head milk production and relative greenhouse gas emissions intensity, compared to a counterfactual farm with similar properties that does not implement the respective intervention.*"}

interventions_scatter_relative<-ggplot(data=interventions_normal_milk,
                        aes(x=milk_change_relative,y=emissions_intensity_change_relative)) +
  geom_point(aes(color=intervention),size=0.9) +
  theme_bw() +
  ggtitle("Intervention impact on milk yield and emissions") + 
  labs(y="Relative change in emissions intensity (%)",
       x="Relative change in per head milk yield (%)",
       color="Intervention") +
  scale_color_manual(values= c("breed" = intervention_colors[1],
                              "nobull" = intervention_colors[2],
                              "lessReplace" = intervention_colors[3],
                              "Calliandra" = intervention_colors[4],
                              "balance" = intervention_colors[6]),
                    labels = c("Breed change", "No bulls", "Fewer males", "Calliandra feed", "Balanced diet")) +
  facet_wrap(~factor(intervention,
                     levels=c("breed","nobull","lessReplace","Calliandra","balance"),
                     labels=c("Breed change", "Retire unproductive bulls", "Fewer replacement males", "Calliandra feed", "Balanced diet"))  ) +
  theme(legend.position = "none")

@@

The herd structure interventions showed potential for causing major changes in milk yields and emissions intensity on particular farms. Plotting these impacts against the initial sets of relevant herd attributes serves to illustrate which farms are particularly responsive to these interventions (Fig. S3).

```{r, fig.dim = c(8, 4), fig.cap="***Figure S5.*** *Influence of the breed composition of farm-scale dairy cow populations on changes in milk yield and emissions intensity of milk production in response to a breed change intervention*."}

@@

melted_breed<-melt(intervention_structures[,c("Farm",
                                              "intervention",
                                              "milk_change_relative",
                                              "emissions_intensity_change_relative",
                                              paste0("breed_",1:8),
                                              "unproductive_bulls",
                                              "replacement_males")],
                   id.vars=c("Farm",
                             "intervention",
                             "milk_change_relative",
                             "emissions_intensity_change_relative",
                             "unproductive_bulls",
                             "replacement_males"))
melted_breed<-melted_breed[which(!is.na(melted_breed$value)),]

@@

metrics <- c("Milk yield per head", "Emissions intensity of milk production")
names(metrics) <- c("milk_change_relative","emissions_intensity_change_relative")

@@

```{r, fig.dim = c(8, 4), fig.cap="***Figure S6.*** *Influence of the percentage of unproductive bulls in a cattle herd on changes in milk yield and emissions intensity of milk production in response to a 'retiring unproductive bulls' intervention*."}

melted_nobull<-melt(intervention_structures[which(intervention_structures$intervention=="nobull"),
                                            c("Farm",
                                              "milk_change_relative",
                                              "emissions_intensity_change_relative",
                                              "unproductive_bulls",
                                              "not_unproductive_bulls")],
                   id.vars=c("Farm",
                             "milk_change_relative",
                             "emissions_intensity_change_relative"))

@@

```{r, fig.dim = c(8, 4), fig.cap="***Figure S7.*** *Influence of the percentage of replacement males in a cattle herd on changes in milk yield and emissions intensity of milk production in response to a 'fewer replacement males' intervention*."}

melted_lessReplace<-melt(intervention_structures[which(intervention_structures$intervention=="lessReplace"),
                                            c("Farm",
                                              "milk_change_relative",
                                              "emissions_intensity_change_relative",
                                              "replacement_males",
                                              "not_replacement_males")],
                   id.vars=c("Farm",
                             "milk_change_relative",
                             "emissions_intensity_change_relative"))

@@

for(i in 1:length(ints))
  {interventions_summary_milk[i,c("Weakest effect",
                                  "5% quantile",
                                  "Median effect",
                                  "95% quantile",
                                  "Strongest effect")]<-
    round(quantile(intervention_structures[which(intervention_structures$intervention==ints[i]),
                                           "milk_change_relative"],c(0,0.05,0.5,0.95,1),
                   na.rm=TRUE),1)
  interventions_summary_emissions[i,c("Weakest effect",
                                      "5% quantile",
                                      "Median effect",
                                      "95% quantile",
                                      "Strongest effect")]<-
    round(quantile(intervention_structures[which(intervention_structures$intervention==ints[i]),
                                           "emissions_intensity_change_relative"],c(1,0.95,0.5,0.05,0),
                   na.rm=TRUE),1)}

@@

```{r, fig.dim = c(8, 4), fig.cap="***Figure 8. *** *Intervention impacts on milk yield and greenhouse gas emissions intensity at an endline sampling point vs. the initial sampling time. The colored background surface indicates the probability that increases in milk productivity are associated with decreasing emissions intensity.*"}

>>>>

```{r, warning=FALSE, message=FALSE,fig.dim = c(8, 4), fig.cap = "***Figure 1.*** *Estimated total emissions from livestock (a) and emission intensity of milk production (b) for a smallholder dairy farm in Kenya. Plausible estimates of both metrics are generated through Monte Carlo simulation, based on 1000 runs of a greenhouse gas emissions model, with uncertainty introduced by specifying inputs as probability distributions. The blue line indicates a precise estimate based on precise results from a farm survey and default parameters recommended by various guidance documents.*"}

@@

farm5b<-ggplot(data=farm5_emissions$y, aes(CO2eq_per_milk)) +
geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") +
  ylab("Relative probability") +
    xlab(expression(Emission~intensity~(kg~CO[2]*'-eq'~kg^-1))) + ggtitle("b) Emission intensity")

@@

```{r, warning=FALSE, message=FALSE, fig.dim = c(8, 4), fig.cap = "***Figure 2.*** *Total greenhouse gas emissions from livestock (a) and emission intensity of milk production (b) across 4140 simulated livestock-keeping households in Kenya (informed by data collected on 414 farms). Plausible estimates of both metrics are generated through Monte Carlo simulation, based on 1000 runs of a greenhouse gas emissions model, with uncertainty introduced by specifying inputs as probability distributions.*"}

@@

all_farms_intensity<-ggplot(data=GHG_simulation_scenarios$y, aes(CO2eq_per_milk)) +
geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") +
  ylab("Relative probability") + theme_bw() +
    xlab(expression(Emission~intensity~(kg~CO[2]*'-eq'~kg^-1))) + ggtitle("b) Emission intensity")

@@

We can now look at summary statistics of total and per head emissions from cattle across livestock-keeping smallholder farms in Kenya. To exclude farms that do not appear to be specializing in livestock, some of which feature extremely high (up to infinity in cases where no milk is produced) emission intensity, we also look at summary statistics across only the farms with per head milk yields of >500 kg of milk.

@@

emissions_summary<-rbind(data.frame("Emissions per farm"=round(quantile(GHG_simulation_scenarios$y$on_farm,
                                                                  c(0,0.05,0.5,0.95,1))/1000,1),
                                    "Emissions per head"=round(quantile(GHG_simulation_scenarios$y$pc_on_farm,
                                                                    c(0,0.05,0.5,0.95,1))/1000,1),
                                    "Emission intensity"=round(quantile(GHG_simulation_scenarios$y$CO2eq_per_milk,
                                                                   c(0,0.05,0.5,0.95,1)),1)),
                         data.frame("Emissions per farm"=round(quantile(dairy_households$y$on_farm,
                                                                  c(0,0.05,0.5,0.95,1))/1000,1),
                                    "Emissions per head"=round(quantile(dairy_households$y$pc_on_farm,
                                                                    c(0,0.05,0.5,0.95,1))/1000,1),
                                    "Emission intensity"=round(quantile(dairy_households$y$CO2eq_per_milk,
                                                                   c(0,0.05,0.5,0.95,1)),1)))
emissions_summary$Quantile<-c("Minimum","5% quantile", "Median", "95% quantile", "Maximum",
                              "Minimum","5% quantile", "Median", "95% quantile", "Maximum")
rownames(emissions_summary)<-NULL

kable(emissions_summary[,c(4,1,2,3)], booktabs = TRUE,
      col.names = c("Distribution attribute",
                    paste0("CO","$_2$","-eq farm","$^{-1}$"),
                    paste0("CO","$_2$","-eq head","$^{-1}$"),
                    paste0("CO","$_2$","-eq kg","$^{-1}$")),
      caption = "<p style='color:black'><i><b>Table S3.</b> Summary statistics of simulated greenhouse gas emissions from cattle across a population of cattle-keeping smallholder farms in Kenya</i></p>") %>% pack_rows(
  index = c("Emissions per farm" = 5, "Emissions per dairy-focused farm" = 5), background="lightgray") %>%
column_spec(2:4, width = "5cm") %>% row_spec(0, align = "c") %>% 
  add_header_above(c(" " = 1, "Emissions per farm" = 1, "Emissions per head" = 1, "Emission intensity" = 1))

@@

We're interested in the suitability of total per head milk production per year as an indicator of the greenhouse gas emission intensity of milk production.

@@

```{r, warning=FALSE, message=FALSE, fig.dim = c(8, 6), fig.cap="***Figure 3.***  *Relationship between milk yield per head (x-axis) and emission intensity of milk production for livestock-keeping smallholder households in Kenya, expressed as a population-level scatter plot (a) and an interpolated probability density surface (b). The vertical lines in (b) illustrate slices through the density surface at productivity levels of 2000 (red) and 3000 (blue) kg milk head^-1^ year^-1^ (the corresponding distributions are shown in Fig. 4b).*"}

plot1 <- ggplot(dairy_households$y, aes(x = pc_milk_yield, y = CO2eq_per_milk)) + 
  geom_point(shape = 20, color = "blue", size = 2) + 
  stat_smooth(method = "loess", fullrange = TRUE) +
  geom_density_2d() +
  geom_rug(color="lightskyblue3") + 
  labs(y=expression(Emission~intensity~of~milk~production~(kg~CO[2]*'-eq'~kg^{-1})),
       x=expression(Milk~yield~per~head~(kg~head^{-1}~year^{-1})))+
  theme_bw() +
  theme(legend.position = c(0.15, 0.9))

@@

densi<-ggplot(dairy_households$y, aes(x = pc_milk_yield, y = CO2eq_per_milk)) +
  stat_density_2d(
    geom = "raster",
    aes(fill = after_stat(density)),
    contour = FALSE
    ) +
  scale_fill_viridis_c() + 
  labs(y=expression(Emission~intensity~of~milk~production~(kg~CO[2]*'-eq'~kg^{-1})),
       x=expression(Milk~yield~per~head~(kg~head^{-1}~year^{-1})),
       fill="Probability \ndensity") +
  theme_bw() + geom_vline(xintercept=c(2000,3000),color=c("#F8766D","#00BFC4"),alpha=.5, lwd=2)

@@

ggsave("figures/Fig_3_scatter_and_surface_per_head_milk_emission_intensity.png",width=10,height=6)

@@

According to these distributions, the emission intensity at a particular per head milk yield can be described by a slice through the probability surface.

```{r varkernelslicerange, message=FALSE, warning=FALSE, fig.dim = c(12, 4), fig.cap="***Figure 4.*** *Greenhouse gas emission intensity of milk production at specific levels of per-head milk production among livestock-keeping smallholder farms in Kenya. Distributions are shown for (a) a production level of 2000 kg milk head^-1^ year^-1^, including a histogram of the random samples the distribution is based on, and (b) production levels of 2000 and 3000 kg milk head^-1^ year^-1^.*"}
slice_2000<-uncertainty::varslice_resample(in_var = dairy_households$y$pc_milk_yield,
                                 out_var = dairy_households$y$CO2eq_per_milk, 
                                 expectedin_var=2000,
                           n = 1000,
                           n_samples = 1000,
                           out_var_sampling = 1000)
slice_3000<-uncertainty::varslice_resample(in_var = dairy_households$y$pc_milk_yield,
                                 out_var = dairy_households$y$CO2eq_per_milk, 
                                 expectedin_var=3000,
                           n = 1000,
                           n_samples = 1000,
                           out_var_sampling = 1000)

one_slice<-ggplot(data=data.frame(CO2eq_per_milk=slice_2000$resampled), aes(CO2eq_per_milk)) +
geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") +
  ylab("Relative probability") +
    xlab(expression(Emission~intensity~at~2000~kg~milk~per~head~(kg~CO[2]*'-eq'~kg^-1))) + theme_bw() + ggtitle("a) Slice through the emission intensity distribution")

@@

two_slices<-ggplot(data=slices, aes(Values, fill=Level)) +
 geom_density(alpha=.2) +
  ylab("Relative probability") +
    xlab(expression(Emission~intensity~at~specific~milk~yield~per~head~(kg~CO[2]*'-eq'~kg^-1))) + labs(fill='Productivity level') + theme_bw() + ggtitle("b) Two slices at different productivity levels")

@@

```{r, fig.dim = c(8, 4), fig.cap="***Figure 5.*** *Probability of a particular farm B featuring lower emission intensity of milk production than another farm A, based on observed per-head milk production levels. Estimates are derived from pairwise comparisons of slices through a population-wide generalization surface of the relationship between per-head milk production and emission intensity. This generalization was generated through Monte Carlo simulation, based on scenarios representing observed production settings on 414 livestock-keeping smallholder farms in Kenya.*"}

@@

ggplot(data = decreased_emissions_probability, aes(Base_yield, new_yield)) + geom_contour_filled(aes(z =
                                                      probability)) +
  ggtitle("Probability of lower emission intensity on farm B") + 
  labs(y=expression(Milk~yield~of~farm~B~(kg~head^{-1}~year^{-1})),
       x=expression(Milk~yield~of~farm~A~(kg~head^{-1}~year^{-1})),
       fill="Probability of \nlower emission \nintensity on farm B") +
  stat_contour(aes(z = probability),breaks = c(0.9),col="black") + 
  theme_bw() +
  scale_x_continuous(limits=c(min(decreased_emissions_probability$Base_yield),NA),expand = c(0, 0)) +
  scale_y_continuous(limits=c(min(decreased_emissions_probability$new_yield),NA),expand = c(0, 0))

ggsave("figures/Fig_5_probability_of_lower_emission_intensity.png", width=7,height=5)

@@

```{r, warning=FALSE, fig.dim = c(8, 4), fig.cap="***Figure S2.*** *Probability of a particular farm B featuring lower emission intensity of milk production than another farm A, based on observed per-head milk production levels (see caption to Fig. 5 for more details). The red line indicates a confidence threshold that is based on the 95% confidence interval of the LOESS regression line shown in Fig. 3a. Using this threshold for predicting changes in emission intensity based on milk yield data would likely lead to a lot of inaccurate classifications.*"}

ggplot(data = decreased_emissions_probability, aes(Base_yield, new_yield)) + geom_contour_filled(aes(z =
                                                      probability)) +
  ggtitle("Probability of lower emission intensity on farm B") + 
  labs(y=expression(Milk~yield~of~farm~B~(kg~head^{-1}~year^{-1})),
       x=expression(Milk~yield~of~farm~A~(kg~head^{-1}~year^{-1})),
       fill="Probability of \nlower emission \nintensity on farm B") +
  stat_contour(aes(z = probability),breaks = c(0.9),col="black") + 
  geom_smooth(data=prediction_data, aes(x=x,y=min_more_milk_loess),col="red")  +  geom_abline(slope=1,intercept=0,linetype = "dashed")  +
  theme_bw() +
  scale_x_continuous(limits=c(min(decreased_emissions_probability$Base_yield),NA),expand = c(0, 0)) +
  scale_y_continuous(limits=c(min(decreased_emissions_probability$new_yield),NA),expand = c(0, 0))

ggsave("figures/Fig_S2_probability_of_lower_emission_intensity.png", width=7,height=5)

@@

```{r, fig.dim = c(8, 8), fig.cap="***Figure S4.*** *Intervention impact on per head milk production and greenhouse gas emission intensity.*"}

@@

interventions[,"milk_change"]<-interventions$pc_milk_yield-interventions$pc_milk_baseline
interventions[,"emission_intensity_change"]<-interventions$CO2eq_per_milk-interventions$CO2_intensity_baseline
interventions[,"milk_change_relative"]<-(interventions$pc_milk_yield-interventions$pc_milk_baseline)/interventions$pc_milk_baseline*100
interventions[,"emission_intensity_change_relative"]<-
  (interventions$CO2eq_per_milk-interventions$CO2_intensity_baseline)/interventions$CO2_intensity_baseline*100

@@

intervention_change <- merge(data.frame(aggregate(interventions_normal_milk$emission_intensity_change,
                                                  by = list(interventions_normal_milk$intervention),
                                                  FUN = mean)),
                             data.frame(aggregate(interventions_normal_milk$milk_change,
                                                  by = list(interventions_normal_milk$intervention),
                                                  FUN = mean)),
                             by = "Group.1")
colnames(intervention_change) <-
  c("intervention", "emission_intensity_change", "milk_change")

@@

interventions_scatter<-ggplot(data=interventions_normal_milk,
                        aes(x=milk_change,y=emission_intensity_change)) +
  geom_point(aes(color=intervention),size=0.9) +
  theme_bw() +
  ggtitle("Intervention impact on milk yield and emissions") + 
  labs(y=expression(Change~'in'~emission~intensity~(kg~CO[2]*'-eq'~kg^-1)),
       x="Change in per head milk yield (kg)",
       color="Intervention") +
  scale_color_manual(values= c("breed" = intervention_colors[1],
                              "nobull" = intervention_colors[2],
                              "lessReplace" = intervention_colors[3],
                              "Calliandra" = intervention_colors[4],
                              "balance" = intervention_colors[6]),
                    labels = c("Breed change", "No bulls", "Fewer males", "Calliandra feed", "Balanced diet")) +
  facet_wrap(~factor(intervention,
                     levels=c("breed","nobull","lessReplace","Calliandra","balance"),
                     labels=c("Breed change", "Retire unproductive bulls", "Fewer replacement males", "Calliandra feed", "Balanced diet"))  ) +
  theme(legend.position = "none")

@@

```{r, fig.dim = c(8, 8), fig.cap="***Figure 6.*** *Intervention impacts on relative per head milk production and relative greenhouse gas emission intensity, compared to a counterfactual farm with similar properties that does not implement the respective intervention.*"}

interventions_scatter_relative<-ggplot(data=interventions_normal_milk,
                        aes(x=milk_change_relative,y=emission_intensity_change_relative)) +
  geom_point(aes(color=intervention),size=0.9) +
  theme_bw() +
  ggtitle("Intervention impact on milk yield and emissions") + 
  labs(y="Relative change in emission intensity (%)",
       x="Relative change in per head milk yield (%)",
       color="Intervention") +
  scale_color_manual(values= c("breed" = intervention_colors[1],
                              "nobull" = intervention_colors[2],
                              "lessReplace" = intervention_colors[3],
                              "Calliandra" = intervention_colors[4],
                              "balance" = intervention_colors[6]),
                    labels = c("Breed change", "No bulls", "Fewer males", "Calliandra feed", "Balanced diet")) +
  facet_wrap(~factor(intervention,
                     levels=c("breed","nobull","lessReplace","Calliandra","balance"),
                     labels=c("Breed change", "Retire unproductive bulls", "Fewer replacement males", "Calliandra feed", "Balanced diet"))  ) +
  theme(legend.position = "none")

@@

The herd structure interventions showed potential for causing major changes in milk yields and emission intensity on particular farms. Plotting these impacts against the initial sets of relevant herd attributes serves to illustrate which farms are particularly responsive to these interventions (Fig. S3).

```{r, fig.dim = c(8, 4), fig.cap="***Figure S5.*** *Influence of the breed composition of farm-scale dairy cow populations on changes in milk yield and emission intensity of milk production in response to a breed change intervention*."}

@@

melted_breed<-melt(intervention_structures[,c("Farm",
                                              "intervention",
                                              "milk_change_relative",
                                              "emission_intensity_change_relative",
                                              paste0("breed_",1:8),
                                              "unproductive_bulls",
                                              "replacement_males")],
                   id.vars=c("Farm",
                             "intervention",
                             "milk_change_relative",
                             "emission_intensity_change_relative",
                             "unproductive_bulls",
                             "replacement_males"))
melted_breed<-melted_breed[which(!is.na(melted_breed$value)),]

@@

metrics <- c("Milk yield per head", "Emission intensity of milk production")
names(metrics) <- c("milk_change_relative","emission_intensity_change_relative")

@@

```{r, fig.dim = c(8, 4), fig.cap="***Figure S6.*** *Influence of the percentage of unproductive bulls in a cattle herd on changes in milk yield and emission intensity of milk production in response to a 'retiring unproductive bulls' intervention*."}

melted_nobull<-melt(intervention_structures[which(intervention_structures$intervention=="nobull"),
                                            c("Farm",
                                              "milk_change_relative",
                                              "emission_intensity_change_relative",
                                              "unproductive_bulls",
                                              "not_unproductive_bulls")],
                   id.vars=c("Farm",
                             "milk_change_relative",
                             "emission_intensity_change_relative"))

@@

```{r, fig.dim = c(8, 4), fig.cap="***Figure S7.*** *Influence of the percentage of replacement males in a cattle herd on changes in milk yield and emission intensity of milk production in response to a 'fewer replacement males' intervention*."}

melted_lessReplace<-melt(intervention_structures[which(intervention_structures$intervention=="lessReplace"),
                                            c("Farm",
                                              "milk_change_relative",
                                              "emission_intensity_change_relative",
                                              "replacement_males",
                                              "not_replacement_males")],
                   id.vars=c("Farm",
                             "milk_change_relative",
                             "emission_intensity_change_relative"))

@@

for(i in 1:length(ints))
  {interventions_summary_milk[i,c("Weakest effect",
                                  "5% quantile",
                                  "Median effect",
                                  "95% quantile",
                                  "Strongest effect")]<-
    round(quantile(intervention_structures[which(intervention_structures$intervention==ints[i]),
                                           "milk_change_relative"],c(0,0.05,0.5,0.95,1),
                   na.rm=TRUE),1)
  interventions_summary_emissions[i,c("Weakest effect",
                                      "5% quantile",
                                      "Median effect",
                                      "95% quantile",
                                      "Strongest effect")]<-
    round(quantile(intervention_structures[which(intervention_structures$intervention==ints[i]),
                                           "emission_intensity_change_relative"],c(1,0.95,0.5,0.05,0),
                   na.rm=TRUE),1)}

@@

```{r, fig.dim = c(8, 4), fig.cap="***Figure 8. *** *Intervention impacts on milk yield and greenhouse gas emission intensity at an endline sampling point vs. the initial sampling time. The colored background surface indicates the probability that increases in milk productivity are associated with decreasing emission intensity.*"}
